\vspace{50pt}\\ \huge \bfseries SKEDGE \\ \vspace{10pt} \Large Smarter course scheduling for our\\ University of Rochester

### 2016-04-13 analytics/usage.tex
Update empty search tables

Figure \ref{fig:searchtypes} validates the hypothesis made in Section 2.3 regarding the search interface design, demonstrating that the \emph{department code} and \emph{course number} search modes dominate user searches, accounting for over 85\% of all searches on Skedge. Bringing the nondistinct field for this in CDCS into prominence is thus a design choice that accomodates empirical usage behavior.

@@

  This type of analysis can powerfully indicate holes in the query language (i.e. searches intuitive for users) that ought to be fixed, which is the same method WolframAlpha describes its team using to improve their freeform input system \cite{wolfram2}. Table \ref{fig:empty-queries} lists a few notable examples of this nature. (Table \ref{fig:funny-queries} lists a few funny queries I came across.)

@@

\singlespacing
{\renewcommand{\arraystretch}{1.5}
\begin{center}
\begin{table}[H]
  \begin{tabular}{ p{6cm} p{7.5cm} }
  \hline

@@

    \hline
  \end{tabular}
  \caption{Example of search queries that produced no results but that indicate demand for added search features. The corresponding features that currently lack in SkedgeQL are described on the right.}
  \label{fig:empty-queries}
\end{table}

\vspace{30pt}

\begin{table}[H]
  \begin{tabular}{ | p{4cm} | p{4cm} | p{4cm} | }
  \hline

    ``{\tt Larry david}''
    & ``{\tt taught by seligman}''
    & ``{\tt cool stuff}''
    \\ \hline

    ``{\tt game of thrones}''
    & ``{\tt interesting courses}''
    & ``{\tt fun classes in csc}''
    \\ \hline

    ``{\tt easy A}''
    & ``{\tt flute birdman}''
    & ``{\tt how do i make a new schedule}''
    \\ \hline

    \hline
  \end{tabular}
  \caption{Humorous search submissions}
  \label{fig:funny-queries}
\end{table}
\end{center}

>>>>

Figure \ref{fig:searchtypes} validates the hypothesis made in Section 2.3 regarding the search interface design, demonstrating that the \emph{department code} and \emph{course number} search modes dominate user searches, accounting for over 85\% of all searches on Skedge. Bringing the nondistinct field for this in CDCS into prominence is thus a design choice that accomodates empirical behavior.

@@

  This type of analysis is powerful, as it can raise issues in the query language (i.e. searches I didn't implement but that users expect to work) with specific fixes. This is the same method WolframAlpha describes its team using to improve their freeform input system \cite{wolfram2}. Table \ref{fig:empty-queries} lists a few notable examples of this nature. (Table \ref{fig:funny-queries} lists a few funny queries I came across.)

@@

\singlespacing
{\renewcommand{\arraystretch}{1.75}
\begin{center}
\begin{table}[H]
\vspace{5pt}
  \begin{tabular}{ p{6cm} p{7.5cm} }

    {\large Empty search examples}
    & {\large Specific fix to SkedgeQL required} \\

    \hline
  \hline

@@

  \end{tabular}
  \caption{Example of search queries that produced no results but that indicate demand for added search features. The corresponding features that currently lack in SkedgeQL are described on the right.}
  \label{fig:empty-queries}
\end{table}

\begin{table}[H]
  \centering
  \begin{tabular}{ l l l }

    \hline

    ``{\tt why 123}''
    & ``{\tt taught by seligman}''
    & ``{\tt cool stuff}''
    \\

    ``{\tt psy cool professor}''
    & ``{\tt interesting courses}''
    & ``{\tt fun classes in csc}''
    \\

    ``{\tt easy A}''
    & ``{\tt flute birdman}''
    & ``{\tt how do i make a new schedule}''
    \\

    \hline

  \end{tabular}
  \vspace{10pt}
  \caption{A sample of humorous searches}
  \label{fig:funny-queries}
\end{table}
\end{center}
